
\documentclass[12pt]{article}
\usepackage{witsa4, witshead, url}
\usepackage{epsfig}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.3ex}
\textheight = 24 cm

\title{Software Design\\Software Documentation Specifications}
\author{\texttt{Team Members} \\Adam Lerumo\\Tumbone Asukile\\Daniel da Silva\\Jan Badenhorst}
\date{\today}
\begin{document}


\makewitshead{School of Computer Science and Applied Mathematics}

\section{Functional requirements ("shall lists")}
\subsection{Medical Practioner Dashboard (login access required)}
The doctor/nurse should be able to update the patients information who is consulting at that time of consultation. The dashboard will also have the following functionalities:
\subsubsection{Patient Profile}
\begin{itemize}
\item \textbf{Patient name}
\item \textbf{Patient Surname}
\item \textbf{Patient Identification Number (Primary search key)}
\item \textbf{Patient Address}
\item \textbf{Patient Next of Kin Contact details}
\item \textbf{Patient details}
\item \textbf{Patient Employment status}
\item \textbf{Patient Mariatal Status}
\item \textbf{Practitioner visited history}
\item \textbf{Patient payment history}
\item \textbf{Patient payment method (e.g medical aid)}
\item \textbf{Patient illeness}
\item \textbf{Patient diagnosis}
\item \textbf{Patient Prescription}
\item \textbf{Patient previous prescriptions from other practitioners ( valid for a certain period )}
\item \textbf{Medication given to patient}
\item \textbf{Patient allergies}
\end{itemize}
\subsubsection{Practice Profile}
\begin{itemize}
\item \textbf{Doctor / Nurse (User Authentication - Required)}
\item \textbf{Practice name}
\item \textbf{Practice number}
\item \textbf{Practice adddress}
\item \textbf{Practice operating hours}
\item \textbf{Invetory available (System should be able to alert if suppliers are low)}
\end{itemize}

\subsection{Systems Admin Dashboard}
It should have all of the functionalities mentiaoned above and the following functionalities:
\subsubsection{Doctor/Nurse Profile (Systems Admin authentication)}
We need this to keep track of which doctor makes changes to the database.
\begin{itemize}
\item \textbf{Doctor Name}
\item \textbf{Doctor Surname}
\item \textbf{Doctor ID number}
\item \textbf{Doctor practice number}
\item \textbf{Doctor contact details}
\item \textbf{Doctor Practice history}
\end{itemize}
\section{Nonfunctional requirements}
\subsection{Usability}
\subsection{Reliability}
\subsection{Performance}
\subsection{Supportability}
\subsection{Implementation}
\subsection{Interface}
\subsection{Packaging}
\subsection{Legal}

\section{Input Requirements}
\subsection{Patient identifier key - ID number}
\subsection{Doctor/Nurse identifier key and user access - Practice Number}
\subsection{System identifier key and user access - ID number}

\section{Process Requirements}
\subsection{Database transaction}
The system must be able to send, receive and trigger transaction to database system.
\subsection{Data integrity}
Commit transactions that are completed and/or rollback unfinished or time-out transactions.
\subsection{Data validation}
Data error from the user’s end and from the back-end database-processing end must be gracefully handled. There will be data validation and error-handling routines as part of the patient registration system.
\subsection{Performance}
Must resolve locking issues and must not allow concurrent access to patient information. Send, receive and display user messages to assist the over-all user experience.
\subsection{Data repository}
The  system will maintain the existing patient information on the database as the main repository of data.
\section{Output Requirements}
\subsection{Transaction summary and confirmation}
\subsection{Exception reports}
System exception reports must be consolidated to record special patient records or special conditions not normally handled .Examples are diabetics, high/low blood pateients, epileptic.
\subsection{Registration Reports and summaries}
System adminstartor and Doctors/nurses must be able to extract summarized and rolled-up data into meaningful
information. All records will be archived but accessible on demand.
\section{Software Requirements}
\subsection{Client Operating Systems}
Windows, Android

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%out of the document%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


